Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2022-01-19 response/referee-response.tex

\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{ragged2e}

\pagenumbering{gobble}

%intsitute command
\usepackage{etoolbox}
\makeatletter
\providecommand{\institute}[1]{% add institute to \maketitle
	\apptocmd{\@author}{\end{tabular}
	\par
	\begin{tabular}[t]{c}
		\small \textit{#1}}{}{}
}
\makeatother

%margins
\usepackage[letterpaper, total={6.5in, 9.5in}]{geometry}

\begin{document}
	\vspace{1in}

	\begin{center}
		{\Large Response to Referee Requests for ``Reaction-diffusion spatial modeling of COVID-19 in Chicago''}
	\end{center}

	\vspace{0.25in}

	I would like to thank the anonymous reviewers of my project writeup, ``Reaction-diffusion spatial modeling of COVID-19 in Chicago'' for their comments and critiques.

	I've revised the paper to address multiple mathematical and form errors, including the presentation of the optimization problem as well as the vector notation.
	I have also included phrases to better introduce some of the mathematics.
	For example, the number of contacts and the diffusion coefficient are now introduced before the presentation of the dynamical system.
	The acronyms for the various epidemic models discussed are now spelled out, as requested.

	Additionally, I've introduced language to hopefully clarify the connection between my project and the values of the SoReMo initiative.
	In truth, I was hoping to obtain better mathematical results, in which case I had planned on including visualizations of inequalities in the city overlayed on the model results.
	I had also hoped to be able to offer suggestions for further use of the model to study how the pandemic interacted with social justice; unfortunately I was forced to offer thoughts on the failure of the model to reproduce the data.

	Lastly, in light of the overall failure of the model, I believe the request to include a discussion of the reasonableness of the parameters is beyond the scope of this project.
	Had the model been successful in describing the propagation of the disease, a discussion of the biological implication of the model would certainly be warranted.
	Since that did not happen, I'm not sure how much value such a discussion would add.
	I think the question of reasonableness is already addressed within the current scope of the project, in that the underlying assumptions about the transmission of the virus need to be revisited.

	\vspace{0.25in}

	\begin{FlushRight}
		Trent Gerew

		\today
	\end{FlushRight}
\end{document}

### 2022-01-19 report/version3.tex
Finalized document
Reorganized folders.
Included referee requests.

\begin{abstract}
	We investigate whether a reaction-diffusion model considering only meanly daily movement is sufficient to describe the spread of the COVID-19 virus in Chicago.
	The model is calibrated using publicly available health data published by the city.
	We first study the system of partial differential equations, then derive the basic reproduction number $\Ro$.
	Then we consider the numerical simulations conducted from March 18 to June 24, 2020.
	Finally, we discuss shortcomings of the model, and offer some potential solutions.
\end{abstract}

\section{Introduction}
	Emerging from Wuhan, China in late 2019, the COVID-19 virus rapidly spread throughout the globe \cite{covid-name}.
	Since the outbreak, governments everywhere have been desperately trying to contain the pandemic.
	Now, with safe and effective vaccines being distributed, it is hoped the pandemic can be overcome \cite{vaccine}.
	Before the introduction of the vaccines, so-called ``non-therapeutic'' interventions \cite{interventions1} were frequently deployed.
	Prominent among these are social distancing, self quarantining, lockdowns, gathering limitations, and the use of personal protective equipment.
	Now with the Omicron variant on the rise \cite{omicron}, these interventions are once again becoming prominent with some European countries reintroducing lockdowns and travel restrictions \cite{lockdowns}.

	Many mathematical models have been proposed to study the spread of the virus.
	Most are compartment models, where a population is divided into groups according to the state of individuals.
	These are generally known as SIR type models.
	The majority of such models ignore any spatial components.
	\cite{s+t+spain} employs a SAIR model and includes mobility terms based on the position of cell phones to model the propagation of the disease through Spain.
	Similarly, \cite{Danon2020.02.12.20022566} incorporates daily movements into an SEIR model.
	In a different approach, \cite{giuliani2020modelling} considers a statistical model to handle diffusion of COVID-19 in Italy.

	Here, we follow \cite{Kevrekidis-2021} and \cite{Mammeri+2020+102+113} in building a virus model where the spatial propagation is modeled by a diffusion and the reactions are derived from an SAIR model.
	Specifically, we examine the spread of COVID-19 in the city of Chicago.
	Does a reaction-diffusion model, which considers only the average daily movements of the population, correctly describe the spread of the virus in Chicago?
	If it does, we can use the model to assess possible vaccination strategies or reopening scenarios.

@@

	\subsection{Mathematical model}
		We focus our study on four components of the epidemic flow (Figure \ref{fig:model}).
		That is, the populations of Susceptible individuals ($S$), Asymptomatic infected individuals ($A$), symptomatic Infected individuals ($I$), and Removed individuals ($R$).
		\begin{figure}[h]
			\centering
			\begin{tikzpicture}
				\node[shape=rectangle, draw=black, fill=green] (s) at (-3,0) {$S$};
				\node[shape=rectangle, draw=black, fill=yellow] (a) at (0,1) {$A$};
				\node[shape=rectangle, draw=black, fill=orange] (i) at (0,-1) {$I$};
				\node[shape=rectangle, draw=black, fill=cyan] (r) at (3,0) {$R$};
				\path[thick,->] (s) edge node[above,swap] {$\omega (\beta_A A + \beta_I I)$} (a);
				\path[thick,->] (a) edge node[right,swap] {$\delta$} (i);
				\path[thick,->] (a) edge node[above,swap] {$\gamma_A$}	(r);
				\path[thick,->] (i) edge node[below,swap] {$\gamma_I$}	(r);
			\end{tikzpicture}
			\caption{Compartmental representation of the SAIR model.}
			\label{fig:model}
		\end{figure}
		Our model is known as the SAIR model \cite{s+t+spain}, which substitutes the $E$ compartment of the SEIR model by the $A$ compartment.
		This model is relevant when there are many undetected asymptomatic infectious individuals, which is known to be the case for COVID-19.

		A few notes motivating this very simple model are necessary.
		\begin{itemize}
			\item
				We do not consider the ``exposed'' $E$ group in this work.
				Because the members of $A$ have separate infection and recovery rates, and because there is a possibility they are detected and move to $I$, we consider $E$ to be merged with $A$.
			\item
				We do not distinguish between quarantined, hospitalized, or nursing home populations.
				Nursing homes are now known to be epicenters of the virus, however the true case rates are notoriously difficult to track \cite{nursing-homes}.
				Additionally, these three population groups can be assumed to be stationary in nature, and in the case of quarantined and hospitalized, isolated.
				Therefore we ignore their individual contributions.
			\item
				In general, the way in which data has been collected and is provided by authorities has varied over time, making its usage rather difficult\footnote{For an in-depth analysis of the data collection problem, see \cite{sara-soremo}.} \cite{messy-data1}, \cite{messy-data2}, \cite{challenges}.
				There is also the question of case counts being influenced by access to testing, especially early in the pandemic.
				Including additional compartments would over-parameterize the model making it more difficult to verify, and would not provide useful information.
			\item
				Lastly, adding additional compartments and parameters reduces the computational feasibility of the optimization problem.
		\end{itemize}
		The goal of this model is to strike a reasonable balance between representation of the pandemic and the populations involved, and feasibility of data collection and computation.

@@

@@

		The parameters $\omega_0$, $\beta_A$, and $\beta_I$ are not independently identifiable, so the optimization problem reduces to five parameters $\theta = (\omega_0 \beta_A, \omega_0 \beta_I, \delta, \gamma_A, \gamma_I)$.
		Given, for $n$ days, the observations $I_\mathrm{obs} (t_i)$, the objective function is the least square function
		\begin{equation} \label{eq:obj}
			J (\theta) = \sum_{i=1}^n \left[ I_\mathrm{obs} (t_i) - I (t_i) \right]^2
		\end{equation}
		with constraints $0 \leq \theta \leq 1$.
		$I (t_i)$ denotes the output of the mathematical model at time $t_i$ computed with parameters $\theta$.

@@

	\subsection{Numerical discretization}
		From the map of the city, the computational domain $\Omega$ is defined as the minimum square enclosing the city.
		The city is contained by $\Omega' = \left\{ (X,Y) \mid X \in [-87.9397, -87.5245], \ Y \in [41.6447, 42.023] \right\}$ where $X$ represents degrees latitude and $Y$ represents degrees longitude.
		Note that degrees latitude and longitude are not equal when converted to miles.
		Therefore, we define the computational domain such that the grid spacing is approximately 0.72 miles in both axes.
		This gives the domain
		\begin{equation} \label{eq:domain}
			\Omega = \left\{ \vec{x} \in \R^2 \mid x \in [0, 40], \ y \in [0, 29] \right\}.
		\end{equation}

@@

\section{Results}
	\subsection{Existence of solutions and basic reproduction numbers}
		We show that we are justified in searching for suitable parameters to solve the model.
		Let $\vec{x} = (S, A, I, R)$ and $\vec{x}_0 = (S_0, A_0, I_0, R_0)$.
		First we show that the solution of the initial value problem (\ref{eq:model}) exists for the case with no diffusion.
		\begin{theorem}
			Let $0 \leq \vec{x}_0 \leq 1$ be the initial datum.
			Then there exists a unique in time solution $\vec{x}$ of the initial value problem (\ref{eq:model}) without diffusion over $C \subset U \subset \R^4 \times \R^1$ where $C$ is a compact set that contains $(\vec{x}_0, t_0)$.
			Moreover, the solution is $\C^1$.
		\end{theorem}
		\begin{proof}
			Since $\vec{x}_t = f(\vec{x},t)$ is $\C^1$ on the open set $U \subset \R^4 \times \R^1$, it follows that there exists a solution of (\ref{eq:model}) without diffusion through the point $\vec{x}_0$ at $t = t_0$ for $|t - t_0|$ sufficiently small.
			Moreover, $\vec{x} (t, t_0,\vec{x_0})$ is a $\C^1$ function \cite{dynamics}.
			Since $C$ is a compact set containing $(\vec{x}_0, t_0)$, then the solution $\vec{x} (t, t_0, \vec{x}_0)$ can be uniquely extended backward and forward in $t$ up to the boundary of $C$ \cite{dynamics}.
		\end{proof}
		\noindent We do provide a proof for the existence of solutions to the initial boundary value problem (\ref{eq:model}) with diffusion terms, but we assume it exists.
		\begin{conjecture}
			Let $0 \leq \vec{x}_0 \leq 1$ the initial datum.
			Then there exists a unique global in time solution $\vec{x}$ of the initial boundary value problem (\ref{eq:model}).
		\end{conjecture}
		\noindent A proof for this conjecture will be similar to the one given in \cite{Mammeri+2020+102+113}.

		An important parameter in understanding the initial growth of the virus is the basic reproduction number.
		\begin{definition}[Basic Reproduction Number]
			The basic reproduction number $\Ro$ can be computed using the next generation of the model without diffusion.
			Since the infected individuals are in $A$ and $I$, new infections ($\mathcal{F}$) and transitions between compartments ($\mathcal{V}$) can be rewritten as
			\begin{align*}
				\mathcal{F} &= \begin{pmatrix} \omega (\beta_A A + \beta_I I) S \\ 0 \end{pmatrix}, &
				\mathcal{V} &= \begin{pmatrix} (\gamma_A + \delta) A \\ \gamma_I - \delta A \end{pmatrix}.
			\end{align*}
			Thus, $\Ro = \rho (\mat{F} \mat{V}^{-1})$ of the next generation matrix
			\begin{equation*}
				\mat{F} \mat{V}^{-1} = \begin{pmatrix} 
				\frac{S_0 \omega_0 \beta_A}{\gamma_A + \delta} + \frac{S_0 \omega_0 \beta_I \delta}{\gamma_I (\gamma_A + \delta)} & 
				\frac{S_0 \omega_0 \beta_I}{\gamma_I} \\ 
				0 & 0 \end{pmatrix}.
			\end{equation*}
			So,
			\begin{equation} \label{eq:ro}
				\Ro =  \frac{S_0 \omega_0}{\gamma_A + \delta}  \left( \beta_A + \beta_I \frac{\delta}{\gamma_I} \right).
			\end{equation}
		\end{definition}
		\noindent This number is dimensionless and has an epidemiological meaning.
		The first term represents the transmission rate by asymptomatic individuals, and the second term represents the transmission rate by symptomatic individuals.

	\subsection{Model resolution}
		Calibration of the model is done from March 18, 2020 to June 24, 2020.
		This range corresponds approximately to the first ``wave'' of cases seen in Chicago.
		The lockdown time points match exactly to the imposed lockdown of the city.
		That is, $t_\mathrm{bol} =$ March 21, 2020 and $t_\mathrm{eol} =$ May 29, 2020.
		In Figure \ref{fig:params}, the table shows the estimated parameters.
		Figure \ref{fig:fit} compares the data and the fitted symptomatic infected populations.
		\begin{figure}[h!]
			\centering
			\begin{subfigure}{0.55\textwidth}
				\begin{tabular}{c c c c}
					\hline
					$\omega_0 \beta_A$ & transmission rate due to $A$ & 0.1969 & days\textsuperscript{-1} \\
					$\omega_0 \beta_I$ & transmission rate due to $I$ & 0.3061 & days\textsuperscript{-1} \\
					$\eta$ & lockdown scale factor & 0.5514 & 1 \\
					$\delta$ & symptom onset rate & 0.0939 & days\textsuperscript{-1} \\
					$\gamma_A$ & removal rate of $A$ & 0.3632 & days\textsuperscript{-1} \\
					$\gamma_I$ & removal rate of $I$ & 0.1385 & days\textsuperscript{-1} \\
					\hline
				\end{tabular}
			\end{subfigure}%
			\begin{subfigure}{0.45\textwidth}
				\includegraphics[width=\textwidth]{box-plot.pdf}
			\end{subfigure}
			\caption{Parameters calibrated according to data from the Chicago Data Portal.
				On the right is a boxplot of the parameter distribution from 1000 optimization iterations.}
			\label{fig:params}
		\end{figure}

@@

\section*{Appendix}
	\subsection*{Nomenclature (Units are indicated in brackets.)}
		\begin{longtable}{c l l}
			\textbf{Latin symbols} & & \\
			$A$ & Asymptomatic infected individuals & [1] \\
			$D$ & Diffusivity & \\
			$I$ & Symptomatic infected individuals & [1] \\
			$J$ & Objective function & N/A \\
			$R$ & Removed individuals & [1] \\
			$\Ro$ & Basic reproduction number & [1] \\
			$S$ & Susceptible individuals & [1] \\
			\textbf{Greek symbols} & & \\
			$\beta_j$ & Contact rate of compartment $j$ & [days\textsuperscript{-1}] \\
			$\gamma_j$ & Recovery rate of compartment $j$ & [days\textsuperscript{-1}] \\
			$\Delta$ & Laplacian operator & N/A \\
			$\delta$ & Rate of asymptomatic individuals that may develop symptoms & [days\textsuperscript{-1}] \\
			$\eta$ & Lockdown scale factor & [1] \\
			$\theta$ & Parameter vector & N/A \\
			$\rho$ & Spectral radius & N/A \\
			$\Omega$ & Computational domain & N/A \\
			$\omega$ & Contacts & [1]
		\end{longtable}

>>>>

\begin{abstract}
	We investigate whether a reaction-diffusion model considering only meanly daily movement is sufficient to describe the spread of the COVID-19 virus in Chicago.
	The model is calibrated using publicly available health data published by the city.
	We first study the system of partial differential equations, then derive the basic reproduction number $\Ro$.
	Then we consider the numerical simulations conducted from March 18 to June 24, 2020.
	These simulations show that this model may not be sufficient to describe COVID-19 in Chicago.
	Finally, we discuss shortcomings of the model, and offer some potential solutions.
\end{abstract}

\section{Introduction}
	Emerging from Wuhan, China in late 2019, the COVID-19 virus rapidly spread throughout the globe \cite{covid-name}.
	Since the outbreak, governments have been trying to contain the pandemic.
	Now, with safe and effective vaccines being distributed, it is hoped the pandemic can be overcome \cite{vaccine}.
	Before the introduction of the vaccines, so-called ``non-therapeutic'' interventions \cite{interventions1} were frequently deployed.
	Prominent among these are social distancing, self quarantining, lockdowns, gathering limitations, and the use of personal protective equipment.
	Now with the Omicron variant on the rise \cite{omicron}, these interventions are once again becoming prominent with some European countries reintroducing lockdowns and travel restrictions \cite{lockdowns}.

	Many mathematical models have been proposed to study the spread of the virus.
	Most are compartment models, where a population is divided into groups according to the state of individuals.
	These are generally known as SIR (susceptible-infected-removed) type models.
	The majority of such models ignore any spatial components.
	\cite{s+t+spain} employs a SAIR (asymptomatic) model and includes mobility terms based on the position of cell phones to model the propagation of the disease through Spain.
	Similarly, \cite{Danon2020.02.12.20022566} incorporates daily movements into an SEIR (exposed) model.
	In a different approach, \cite{giuliani2020modelling} considers a statistical model to handle diffusion of COVID-19 in Italy.

	The goal of our model is to strike a reasonable balance between representation of the pandemic and the populations involved, and feasibility of data collection and computation.

	To do this, we follow \cite{Kevrekidis-2021} and \cite{Mammeri+2020+102+113} in building a virus model where the spatial propagation is modeled by a diffusion and the reactions are derived from an SAIR model.
	Specifically, we examine the spread of COVID-19 in the city of Chicago.
	Does a reaction-diffusion model, which considers only the average daily movements of the population, correctly describe the spread of the virus in Chicago?
	If it does, we can use the model to assess possible vaccination strategies or reopening scenarios.

	A successful model can also be used to examine how social and economic disparities play a role in the transmission of COVID-19.
	One can merge race, income, or health-care accessibility data from the Chicago area with the results from the model to ask and hopefully answer questions like the following:
	Does community structure play a role?
	How effective are vaccines? (Or what is thwarting them?)
	Are care facilities properly allocated?

@@

	\subsection{Mathematical model}
		We focus our study on four components of the epidemic flow (Figure \ref{fig:model}).
		That is, the populations of Susceptible individuals ($S$), Asymptomatic infected individuals ($A$), symptomatic Infected individuals ($I$), and Removed individuals ($R$).
		\begin{figure}[h]
			\centering
			\begin{tikzpicture}
				\node[shape=rectangle, draw=black, fill=green] (s) at (-3,0) {$S$};
				\node[shape=rectangle, draw=black, fill=yellow] (a) at (0,1) {$A$};
				\node[shape=rectangle, draw=black, fill=orange] (i) at (0,-1) {$I$};
				\node[shape=rectangle, draw=black, fill=cyan] (r) at (3,0) {$R$};
				\path[thick,->] (s) edge node[above,swap] {$\omega (\beta_A A + \beta_I I)$} (a);
				\path[thick,->] (a) edge node[right,swap] {$\delta$} (i);
				\path[thick,->] (a) edge node[above,swap] {$\gamma_A$}	(r);
				\path[thick,->] (i) edge node[below,swap] {$\gamma_I$}	(r);
			\end{tikzpicture}
			\caption{Compartmental representation of the SAIR model.}
			\label{fig:model}
		\end{figure}

		Our model is known as the SAIR model \cite{s+t+spain}, which substitutes the $E$ compartment of the SEIR model by the $A$ compartment.
		This model is relevant when there are many undetected asymptomatic infectious individuals, which is known to be the case for COVID-19.

		A few notes motivating this very simple model are necessary.
		\begin{itemize}
			\item
				We do not consider the ``exposed'' $E$ group in this work.
				Because the members of $A$ have separate infection and recovery rates, and because there is a possibility they are detected and move to $I$, we consider $E$ to be merged with $A$.
			\item
				We do not distinguish between quarantined, incarcerated, hospitalized, or nursing home populations.
				Nursing homes are now known to be epicenters of the virus, however the true case rates are notoriously difficult to track \cite{nursing-homes}.
				Additionally, these four population groups can be assumed to be stationary in nature, and in the case of quarantined and hospitalized, isolated.
				Therefore we ignore their individual contributions.
			\item
				In general, the way in which data has been collected and is provided by authorities has varied over time, making its usage rather difficult\footnote{For an in-depth analysis of the data collection problem, see \cite{sara-soremo}.} \cite{messy-data1}, \cite{messy-data2}, \cite{challenges}.
				There is also the question of case counts being influenced by access to testing, especially early in the pandemic.
				Including additional compartments would over-parameterize the model making it more difficult to verify, and would not provide useful information.
			\item
				Lastly, adding additional compartments and parameters reduces the computational feasibility of the optimization problem.
		\end{itemize}

@@

		The average number of contacts $\omega$ is described in Equation \ref{eq:contacts}.
		The diffusion coefficient $D$ is assumed to be the same for both $A$ and $I$, and is defined by Equation \ref{eq:diffusion}.

@@

		The parameters $\omega_0$, $\beta_A$, and $\beta_I$ are not independently identifiable, so the optimization problem reduces to five parameters $\vec{\theta} = (\omega_0 \beta_A, \omega_0 \beta_I, \delta, \gamma_A, \gamma_I)$.
		Given the observations $I_\mathrm{obs} (t_i)$ over $n$ days, we have the minimization problem
		\begin{equation} \label{eq:obj}
			\begin{aligned}
				\min_\theta \quad & \sum_{i=1}^n \left[ I_\mathrm{obs} (t_i) - I (t_i) \right]^2 \\
				\textrm{s.t.} \quad & \vec{0} \leq \theta \leq \vec{1}
			\end{aligned}
		\end{equation}
		$I (t_i)$ denotes the output of the mathematical model at time $t_i$ computed with parameters $\vec{\theta}$.

@@

	\subsection{Numerical discretization}
		From the map of the city, the computational domain $\Omega$ is defined as the minimum square enclosing the city.
		The city is contained by $\Omega' = \left\{ (X,Y) \mid X \in [-87.9397, -87.5245], \ Y \in [41.6447, 42.023] \right\}$ where $X$ represents degrees latitude and $Y$ represents degrees longitude.
		Note that degrees latitude and longitude are not equal when converted to miles.
		Therefore, we define the computational domain such that the grid spacing is approximately 0.72 miles in both axes.
		This gives the domain
		\begin{equation*} \label{eq:domain}
			\Omega = \left\{ \vec{x} \in \R^2 \mid x \in [0, 40], \ y \in [0, 29] \right\}.
		\end{equation*}

@@

\section{Results}
	\subsection{Existence of solutions and basic reproduction numbers}
		We show that we are justified in searching for suitable parameters to solve the model.
		Let $\vec{x} = (S, A, I, R)^\intercal$ and $\vec{x}_0 = (S_0, A_0, I_0, R_0)^\intercal$.
		First we show that the solution of the initial value problem (\ref{eq:model}) exists for the case with no diffusion.
		\begin{theorem}
			Let $\vec{0} \leq \vec{x}_0 \leq \vec{1}$ be the initial datum.
			Then there exists a unique in time solution $\vec{x}$ of the initial value problem (\ref{eq:model}) without diffusion over $C \subset U \subset \R^4 \times \R^1$ where $C$ is a compact set that contains $(\vec{x}_0, t_0)$.
			Moreover, the solution is $\C^1$.
		\end{theorem}
		\begin{proof}
			Since $\vec{x}_t = f(\vec{x},t)$ is $\C^1$ on the open set $U \subset \R^4 \times \R^1$, it follows that there exists a solution of (\ref{eq:model}) without diffusion through the point $\vec{x}_0$ at $t = t_0$ for $|t - t_0|$ sufficiently small.
			Moreover, $\vec{x} (t, t_0,\vec{x_0})$ is a $\C^1$ function \cite{dynamics}.
			Since $C$ is a compact set containing $(\vec{x}_0, t_0)$, then the solution $\vec{x} (t, t_0, \vec{x}_0)$ can be uniquely extended backward and forward in $t$ up to the boundary of $C$ \cite{dynamics}.
		\end{proof}
		\noindent We do not provide a proof for the existence of solutions to the initial boundary value problem (\ref{eq:model}) with diffusion terms, but we assume it exists.
		\begin{conjecture}
			Let $\vec{0} \leq \vec{x}_0 \leq \vec{1}$ the initial datum.
			Then there exists a unique global in time solution $\vec{x}$ of the initial boundary value problem (\ref{eq:model}).
		\end{conjecture}
		\noindent A proof for this conjecture will be similar to the one given in \cite{Mammeri+2020+102+113}.

		An important parameter in understanding the initial growth of the virus is the basic reproduction number.
		\begin{definition}[Basic Reproduction Number]
			The basic reproduction number $\Ro$ can be computed using the next generation of the model without diffusion.
			Since the infected individuals are in $A$ and $I$, new infections ($\mathcal{F}$) and transitions between compartments ($\mathcal{V}$) can be rewritten as
			\begin{align*}
				\mathcal{F} &= \begin{pmatrix} \omega (\beta_A A + \beta_I I) S \\ 0 \end{pmatrix}, &
				\mathcal{V} &= \begin{pmatrix} (\gamma_A + \delta) A \\ \gamma_I - \delta A \end{pmatrix}.
			\end{align*}
			Then $\mat{F}$ and $\mat{V}$ are the Jacobians of $\mathcal{F}$ and $\mathcal{V}$ respectively evaluated at the disease free equilibrium.
			Thus, $\Ro = \rho (\mat{F} \mat{V}^{-1})$ of the next generation matrix
			\begin{equation*}
				\mat{F} \mat{V}^{-1} = \begin{pmatrix} 
				\frac{S_0 \omega_0 \beta_A}{\gamma_A + \delta} + \frac{S_0 \omega_0 \beta_I \delta}{\gamma_I (\gamma_A + \delta)} & 
				\frac{S_0 \omega_0 \beta_I}{\gamma_I} \\ 
				0 & 0 \end{pmatrix}.
			\end{equation*}
			So,
			\begin{equation*} \label{eq:ro}
				\Ro =  \frac{S_0 \omega_0}{\gamma_A + \delta}  \left( \beta_A + \beta_I \frac{\delta}{\gamma_I} \right).
			\end{equation*}
		\end{definition}
		\noindent This number is dimensionless and has an epidemiological meaning.
		The first term represents the transmission rate by asymptomatic individuals, and the second term represents the transmission rate by symptomatic individuals.

	\subsection{Model resolution}
		Calibration of the model is done from March 18, 2020 to June 24, 2020.
		This range corresponds approximately to the first ``wave'' of cases seen in Chicago.
		The lockdown time points match exactly to the imposed lockdown of the city.
		That is, $t_\mathrm{bol} =$ March 21, 2020 and $t_\mathrm{eol} =$ May 29, 2020.
		In Figure \ref{fig:params}, the table shows the estimated parameters.
		Figure \ref{fig:fit} compares the data and the fitted symptomatic infected populations.
		\begin{figure}[h!]
			\centering
			\begin{subfigure}{0.55\textwidth}
				\begin{tabular}{c c c c}
					\hline
					$\omega_0 \beta_A$ & transmission rate due to $A$ & 0.1969 & days\textsuperscript{-1} \\
					$\omega_0 \beta_I$ & transmission rate due to $I$ & 0.3061 & days\textsuperscript{-1} \\
					$\eta$ & lockdown scale factor & 0.5514 & 1 \\
					$\gamma_A$ & removal rate of $A$ & 0.3632 & days\textsuperscript{-1} \\
					$\gamma_I$ & removal rate of $I$ & 0.1385 & days\textsuperscript{-1} \\
					$\delta$ & symptom onset rate & 0.0939 & days\textsuperscript{-1} \\
					\hline
				\end{tabular}
			\end{subfigure}%
			\begin{subfigure}{0.45\textwidth}
				\includegraphics[width=\textwidth]{box-plot.pdf}
			\end{subfigure}
			\caption{Parameters calibrated according to data from the Chicago Data Portal.
				On the right is a boxplot of the parameter distribution from 1000 optimization iterations.}
			\label{fig:params}
		\end{figure}

@@

	\vspace{0.5cm}

	\noindent \textbf{Acknowledgments:} The author would like to thank the anonymous reviews for their comments.

\section*{Appendix}
	\subsection*{Nomenclature (Units are indicated in brackets.)}
		\begin{longtable}{c l l}
			\textbf{Latin symbols} & & \\
			$A$ & Asymptomatic infected individuals & [1] \\
			$D$ & Diffusivity & \\
			$\mathcal{F}$ & Rate of appearance of new infections & [days\textsuperscript{-1}] \\
			$\mat{F}$ & Jacobian of $\mathcal{F}$ evaluated at the disease-free equilibrium & N/A \\
			$I$ & Symptomatic infected individuals & [1] \\
			$R$ & Removed individuals & [1] \\
			$\Ro$ & Basic reproduction number & [1] \\
			$S$ & Susceptible individuals & [1] \\
			$\mathcal{V}$ & Rate of transfer of individuals & [days\textsuperscript{-1}] \\
			$\mat{V}$ & Jacobian of $\mathcal{V}$ evaluated at the disease-free equilibrium & N/A \\
			\textbf{Greek symbols} & & \\
			$\beta_j$ & Contact rate of compartment $j$ & [days\textsuperscript{-1}] \\
			$\gamma_j$ & Recovery rate of compartment $j$ & [days\textsuperscript{-1}] \\
			$\Delta$ & Laplacian operator & N/A \\
			$\delta$ & Rate of asymptomatic individuals that may develop symptoms & [days\textsuperscript{-1}] \\
			$\eta$ & Lockdown scale factor & [1] \\
			$\theta$ & Parameter vector & N/A \\
			$\rho$ & Spectral radius & N/A \\
			$\Omega$ & Computational domain & N/A \\
			$\omega$ & Contacts & [1]
		\end{longtable}
